Debugging by {\huge\bf\textit{lastChange}}

### 2011-03-08 papers/fse2011/sig-alternate.tex

@@

@@

@@

>>>>

Program slicing\cite{Weiser} approaches debugging from a completely different perspective. Given a point of interest {\bf S} in a program, a \textit{slice} is an executable subset of the program affecting {\bf S}.  Many studies have shown ways to compute the slice more quickly or to constrain the slice to a smaller subset of the program \cite{Horwitz, Sridharan}.  Dynamic slicing \cite{Korel} applies slicing analysis at run time and thus most closely resembles lastChange from among the slicing approaches.  Our lastChange approach can be related this way: first, allow the developer to select from {\bf S} a key critical value {\bf V}. Then compute a slice affecting {\bf V}. Show the developer only the most relevant part of that slice (the lastChange). Finally iterate towards the fault by chaining new slice-selection criteria.

Both approaches rely on selecting {\bf S}. Both approaches differ from breakpoint debugging in analyzing a program from a known good point (e.g. start of the program) to {\bf S}.  Slicing reduces the space the developer needs to search, but provides no guidance within the slice; lastChange explores the slice using developer-selected search criteria, but does not help the developer recognize code that cannot impact {\bf S}. Slicing requires a sophisticated compiler-like technology while lastChange builds on familiar run-time debugger technology.

@@

\bibitem{Horwitz}%[Hofer(2006)]
S. Horwitz, B. Liblit, and M. Polishchuk. \newblock Better Debugging via Output Tracing and Callstack-Sensitive Slicing.
\emph{IEEE Transactions on
Software Engineering}, 36(1):7-19, 2010.

@@

\bibitem{Korel}%[Ko(2008)]
B. Korel and J. Laski. \newblock Dynamic Program Slicing.
\newblock \emph{Information Processing Letters},
 29(3):155-163, 1988.

@@

\bibitem{Sridharan}%[Boothe(2000)]
M. Sridharan, S.J. Fink , and R. Bodik. \newblock Thin slicing.
\newblock In \emph{Conference on Programming Language Design and Implementation(PLDI)},
June, 2007.
